\huge The human visual system preserves the hierarchy of 2-dimensional pattern regularity

### 2021-03-10 Writeup/kohler_clarke_2021.tex
fixed typo in citation.

\documentclass[11pt, twoside]{article}
\usepackage{boisik}
\usepackage[OT1]{fontenc}
\usepackage[affil-it]{authblk}
\usepackage{graphicx}
\usepackage{multicol}
\usepackage{hyperref}
\hypersetup{colorlinks=false}
\usepackage{natbib}
\usepackage{geometry}
\usepackage{amsmath}
 \geometry{a4paper, total={170mm,257mm}, left=20mm, top=20mm}

@@

We observe a reliable correlation between our brain imaging and psychophysical data. This suggests that the two measurements reflect the same underlying symmetry representations in visual cortex. While it should be noted that the correlation is relatively modest ($R^2 = 0.44$), we note that this may be partly due to the fact that the same individuals did not participate in the two experiments. Future work in which behavioral and brain imaging data are collected from the same participants, will help further establish the connection between the two measurements, and tease apart any additional complexity that may not have been captured by the summary statistics we applied here. It has recently been demonstrated that \textit{W}, a measure of perceptual goodness derived from a holographic model of regularity \citep{van_der_helm_1996}, can predict EEG responses \citep{makin_w_2016} and perceptual discrimination performance \citep{nucci_2007} for patterns that contain symmetry and other types of regularity. The model was formulated based on dot patterns with symmetry axes centered on a single spatial location. It will important to determine if and how \textit{W} can computed for our random-noise based wallpaper textures where combinations of symmetries tile the plane, and test how well it can explain behavioral and brain responses to wallpapers.

@@

Bayesian analysis was carried out using R (v3.6.1) \citep{R} with the \texttt{brms} package (v2.9.0) \citep{burkner2017} and rStan (v2.19.2 \citep{rStan}). The data from each experiment were modelled using a Bayesian generalised mixed effect model with wallpaper group being treated as a 16 level factor, and random effects for participant. The SSVEP data and symmetry detection threshold durations were modelled using log-normal distributions with weakly informative, $ \mathcal{N}(0, 2)$, priors. After fitting the model to the data, samples were drawn from the posterior distribution of the two datasets, for each wallpaper group. These samples were then recombined to calculate the distribution of differences for each of the 63 pairs of subgroup and supergroup. These distributions were then summarised by computing the conditional probability of obtaining a positive (negative) difference, $p(\Delta | \text{data})$. For further technical details, please see the Supplementary Materials at \url{https://osf.io/f3ex8/} where the full R code, model specification, prior and posterior predicitive checks, and model diagnoastics, can be found.

>>>>

\documentclass[11pt, twoside]{article}
\usepackage{boisik}
\usepackage[OT1]{fontenc}
\usepackage[affil-it]{authblk}
\usepackage{graphicx}
\usepackage{multicol}
\usepackage{natbib}
\usepackage{geometry}
\usepackage{amsmath}
 \geometry{a4paper, total={170mm,257mm}, left=20mm, top=20mm}

@@

We observe a reliable correlation between our brain imaging and psychophysical data. This suggests that the two measurements reflect the same underlying symmetry representations in visual cortex. While it should be noted that the correlation is relatively modest ($R^2 = 0.44$), we note that this may be partly due to the fact that the same individuals did not participate in the two experiments. Future work in which behavioral and brain imaging data are collected from the same participants, will help further establish the connection between the two measurements, and tease apart any additional complexity that may not have been captured by the summary statistics we applied here. It has recently been demonstrated that \textit{W}, a measure of perceptual goodness derived from a holographic model of regularity \citep{van_der_helm_1996}, can predict EEG responses \citep{makin_2016} and perceptual discrimination performance \citep{nucci_2007} for patterns that contain symmetry and other types of regularity. The model was formulated based on dot patterns with symmetry axes centered on a single spatial location. It will important to determine if and how \textit{W} can computed for our random-noise based wallpaper textures where combinations of symmetries tile the plane, and test how well it can explain behavioral and brain responses to wallpapers.

@@

Bayesian analysis was carried out using R (v3.6.1) \citep{R} with the \texttt{brms} package (v2.9.0) \citep{burkner2017} and rStan (v2.19.2 \citep{rStan}). The data from each experiment were modelled using a Bayesian generalised mixed effect model with wallpaper group being treated as a 16 level factor, and random effects for participant. The SSVEP data and symmetry detection threshold durations were modelled using log-normal distributions with weakly informative, $ \mathcal{N}(0, 2)$, priors. After fitting the model to the data, samples were drawn from the posterior distribution of the two datasets, for each wallpaper group. These samples were then recombined to calculate the distribution of differences for each of the 63 pairs of subgroup and supergroup. These distributions were then summarised by computing the conditional probability of obtaining a positive (negative) difference, $p(\Delta | \text{data})$. For further technical details, please see the Supplementary Materials at \texttt{https://osf.io/f3ex8/} where the full R code, model specification, prior and posterior predicitive checks, and model diagnoastics, can be found.
